Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-18 paper/paper.tex
rewrote correlation programs to do things a better way.  added data necc for committing, changed makefile to demand these data files, change the correlation included in paper accordingly Tested everything on quipu.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{No caption}
  \label{corr-pill}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation-rl.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{Correlation for A shapes}
  \label{fig:corr-pancake-A}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation-rl.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation-rl.pdf}
  \caption{Correlation for B shapes}
  \label{corr-B}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
  \caption{No caption}
  \label{corr-pill}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
  \caption{Correlation for A shapes}
  \label{fig:corr-pancake-A}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
  \caption{Correlation for B shapes}
  \label{corr-B}
\end{figure}
